A note on the instability and degeneracy of deep learning models

### 2016-10-24 writing/note.Rmd
clean up

---
title: "A note on the instability and degeneracy of deep learning models"
author: "Andee Kaplan, Daniel Nordman, Stephen Vardeman"
date: "October, 2016"
linestretch: 2
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    number_sections: yes
bibliography: references/refs.bib
abstract: |
  We introduce a broad class of discrete space models that are defined in relation to how a probability model is built to incorporate more variables. We will call this class of models *Discrete Expanding Finite space*, or DEF models. They are defined as models in discrete finite space with a sequence of expanding model parameter vectors that potentially grow size as the dimension of the data become larger and model support equal the sample space. In this paper, we present results that define the notion of model instability as well as near-degeneracy within the framework of DEF models in addition to demonstrating example models of the DEF class.
---

@@

This paper is structured as follows. First, in Section \ref{examples}, we present specific examples of DEF models and discuss how they fit in this framework (including deep learning models). Section \ref{instability-and-degeneracy-results} establishes some formal results regarding the model propriety of DEF models. Lastly, Section \ref{implications} emphasizes the implications of our model prepriety results.

>>>>

---
title: "A note on the instability and degeneracy of deep learning models"
author: "Andee Kaplan, Daniel Nordman, Stephen Vardeman"
date: "October, 2016"
linestretch: 2
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    number_sections: yes
bibliography: references/refs.bib
abstract: |
  We introduce *Discrete Expanding Finite space*, or DEF models, a broad class of discrete space models that are defined in relation to how a probability model is built to incorporate more variables. These models are defined to be in discrete finite space with model support equal the sample space and with a sequence of expanding model parameter vectors that potentially grow size as the dimension of the data become larger. In this paper, we present results that define the notion of model instability as well as near-degeneracy within the framework of DEF models in addition to demonstrating example models of the DEF class.
---

@@

This paper is structured as follows. First, in Section \ref{examples}, we present specific examples of DEF models and discuss how they fit in this framework (including deep learning models). Section \ref{instability-and-degeneracy-results} establishes formal results regarding the model propriety of DEF models. Lastly, Section \ref{implications} emphasizes the implications of our model propriety results.
